The nature that determine an anime show's popularity involves the source material of the adaptation and the years it was released.

### 2023-04-21 outputs/paper/paper.qmd
- Fixed YAML of all script files - Updated .Rproj name to reflect project name - Updated Quarto document with more content and graphs - Saved a model as an .rds and saved in new models folder in outputs

---
title: The multifaceted nature that determine an anime show's popularity involves (findings of the paper, WIP).
author: 
  - Justin Abando
thanks: "Code and data are available at: https://github.com/justabando/malanalysis."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "There are online lists and forums where users can vote on what they believe to be the most popular anime such as MyAnimeList (MAL). However, there are no metrics to determine why specific anime stand out, with some shows being rated lower in terms of quality, yet have more popularity based on MAL user responses. Data was retrieved to determine what factors could be responsible for a show's popularity. It was found that (results of analysis, WIP). The findings of this paper suggests reasons why a particular anime becomes popular, which can be relevant to those that are new to watching anime or those that want something new to watch as they would gravitate to shows that receive traction by a broader demographic."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(janitor)
library(ggplot2)
library(knitr)
library(kableExtra)

@@

  (EDIT) This presents two ways for newcomers to judge a show before watching. They can be inclined to start a show that is subjectively rated as one of the best as ranked by the MAL community, or choose one that has gained the most traction despite any apparent flaws or drawbacks that may deter a positive watching experience. As such, it should be noted that popularity is not a metric that is inherently positive, but can also imply the notorious status of a show, especially if it is ranked low in terms of rating but manages to be much more popular than its rating score suggests. This creates an interesting method to identify shows that have managed to be popular despite its poor ranking performance. It could be that the show has notoriously bad traits that often gets shared to others to ridicule or prank unsuspecting friends to watch and experience a show that can be "so bad that its good". The anime may have been able to maintain a good quality throughout its run time, but eventually hit a point in the plot that polarizes the show's watchers. Regardless, there are many ways to interpret the collective opinion of a show on MAL with the presence of ranking both its ratings and popularity. While the rating of a show is indicative of how well-received the show is strictly by the subject and content of the show itself, the popularity of a show can be shrouded in mystery and depend on many logistical factors the put an anime in the limelight.

@@

  It was found that (the results of paper, WIP).

  (EDIT) The findings of this paper suggest that the popularity of a show is influenced by a variety of factors that may not be obvious by just watching the show itself. These findings can help someone who is new to watching anime, or those that want something new to watch to find something that gained traction within the community. Popularity can be a factor that is more important than the ranking of the show's quality in many cases, and this is due to the context that the show presents. An anime may be very well-received, but it may be less known within the broader community due to subject matter that may be difficult to process, whether it would be highly philosophical, graphic, or leans in any other kind of extreme direction that may lose the interest of a casual viewer. With less overall viewership of an anime, the show may still be ranked relatively high in terms of rating due to its niche community that watches the show, which can inflate its overall ranking in its ratings. This is why ratings are not necessarily the best metric to depend on for newcomers to find a show to watch, as a niche show may not be widely accessible to a broad audience. However, popularity ranking can be much more indicative of a potential show someone can watch due to its exposure that is not dependent on the taste or bias of the viewer. As such, the (factors that influence popularity that will be discussed on, WIP).

@@

Regardless, data from MAL was imported and analyzed in R [@r2023]. To aid in this analysis, the `dplyr` [@wickham2023] and `ggplot2` [@wickham2016] packages from the `tidyverse` package [@wickham2019] were used to clean the data set and generate graphs to visualize it respectively. The `knitr` [@xie2021] and `kableExtra` [@zhu2021] packages were used to create the tables used within this analysis.

@@

* `title`: the title of the anime.
* `type`: the medium of how the anime is delivered (e.g. tv show, movie, etc.).
* `score`: aggregated score of the anime out of 10, contributed by users of MAL that both have the anime in their list as well as rated it numerically out of 10.
* `scored_by`: the number of MAL users that have the anime in their list and rated the anime out of 10.
* `members`: the number of MAL users that have the anime in their list.
* `episodes`: the number of episodes that a given anime has.
* `source`: the type of source material that the anime was adapted from (e.g. manga, light novel, anime original, etc.).
* `start_year`: the year in which the anime first started to broadcast.
* `studios`: the names of the studios that produced the anime.

The important variable of note to consider from this list is `members`. This is a quantitative variable that popularity ranking on MAL is completely dependent on. Other than `title`, the rest of the variables will be tested to see if they have any kind of influence on the amount of users that have specific shows on their lists.

@@

animeinformationsummary |>
  kable(
    caption = "Sample from the top rated anime of MAL, which includes the information of each anime itself.",
    col.names = c("Rank",
                  "Title",
                  "Show Type",
                  "Episode Count",
                  "Source Material",
                  "Start Year",
                  "Studios"),
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(font_size = 10) |>
  column_spec(2, width = "4cm") |>
  column_spec(3, width = "1cm") |>
  column_spec(4, width = "1cm") |>
  column_spec(5, width = "1.5cm") |>
  column_spec(6, width = "1cm") |>
  column_spec(7, width = "3cm")

@@

The main variables of interest as mentioned previously are medium of the show, episode count, source material, initial release year, studios, and licensors. These are all important and can possibly influence the popularity of an anime without giving any actual information of what the anime is about. First, a visualization of how viewership is impacted depending on how old an anime is can be seen in @fig-memberyear.

@@

It can be seen that there are considerable more entries of anime in general, as more shows were produced in the 1970s [@fig-memberyear]. However, there does seem to be more MAL users that watch shows around past the year 2000 mark. Meanwhile, MAL viewership for anime produced before 1975 are rarely seen in comparison.

```{r}
#| label: fig-
#| fig-cap: N/A
#| echo: false
#| warning: false

A multiple linear regression model can be used to predict how each of the qualitative independent factors (show type, episode count, start year, source material, studios) can affect how many users of MAL watch a given anime.

cleanedanime2$type <-as.factor(cleanedanime2$type)
anime_model <- lm(members ~ episodes, data = cleanedanime2)

summary(anime_model)

@@

@@

@@

	- Each instance in the dataset represent an anime entry within the MAL database.

@@

	- There are a total of 24,165 observations, each representing a different show.

@@

	- The dataset is a sample of instances. It is obtained through convenience sampling from the larger set of Black Desert Online players on the North American and European servers. Since the dataset is obtained through convenience sampling, it is not representative of the total population in terms fof geographical coverage or any stratification. The choice of convenience sampling is due to the lack of APIs and useful tracking tools provided by Pearl Abyss, the developers behind Black Desert Online.

@@

	-  Each instance of data consists of a player's age, gender, total playtime in the game and on their main character, their rated importance of various subscription items in the game, and their total spending on various types of items in the game.

@@

	- the gender is either male, female, or other.

@@

	- There is lack of female and other genders in certain age groups in the dataset due to insufficient sample size.

@@

	- There are no relationships between individual instances.

@@

@@

	- The sample size is unequal for female and male respondents. This unequal sample size does negatively affect the assumption of equal variances. Furthermore, lack of detailed statistic tracking tools and APIs provided by Pearl Abyss--the developer of Black Desert Online--means that playtime and most monetary questions in the survey rely on the respondents' best estimates. 

@@

	- Breakdown of the monetary transcations of each player might be considered a confidential data by Pearl Abyss. However, the survey was designed to be as transparent with the respondents as possible, and no data that could be linked back to the respondents were included in the survey nor in the final paper.

@@

	- The dataset does not contain any offensive or insulting data.

@@

	- The datasets are split by age groups and gender as self-identified by the respondents.

@@

	- It is entirely impossible to identify individuals from the dataset.

@@

	- The datasets do not contain data that might be considered sensitive in any way.

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online. The data was reported by the respondents based on their best estimates.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online. The data was reported by the respondents based on their best estimates. Google Forms is used to produce the survey.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Convenience sampling was used due to lack of detailed statistic tracking tools and APIs provided by Pearl Abyss.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- No one but the author is involved in the data collection process.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was collected over the span of four days from April 18, 2022 to April 21, 2022.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No ethical review processes were conducted. Subreddit moderators were consulted for permission of posting the survey.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected through a survey distributed to the subreddit page of Black Desert Online, the official website's forum of Black Desert Online, and the steam discussion page of Black Desert Online.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- Respondents were informed of the purpose of the data collection: "I wish to study the different monetization methods that BDO employs. Due to the lack of proper APIs provided by Pearl Abyss, I have resorted to surveys instead."
	- "To be clear, there will not be any information present in the final paper that can be used to link the data back to the original respondents."
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Since data collection is through a survey, consent was explicitly provided when respondents clicked the survey link.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Respondents can revoke consent by simply exiting the survey.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A.
12. *Any other comments?*

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Certain variables names were shortened in Google Spreadsheet before the dataset is used for analysis in this paper.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is accessable in the github link provided in this paper.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- statistical programming language R [@citeR] was used to preprocess the datasets.
	- Google Spreadsheet is publicly available for use by registering a Google account.
4. *Any other comments?*
	- None.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- At the time of writing this, only this paper has utilized the dataset.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The repository for this paper, which uses the datasets, are available at https://github.com/zhan7818/bdo_monetization.
3. *What (other) tasks could the dataset be used for?*
	- The datasets could be used to modeling or finding relationship between total in-game spending and age groups.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- None.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- The datasets should not be used in an effort to harass or discriminate against the general Black Desert Online community nor should it be used to misrepresent information about the said community.
6. *Any other comments?*
	- None.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Since there dataset is publicly available through the github link, yes.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed on Tian Yi Zhang's github page, along with this paper: https://github.com/zhan7818/bdo_monetization.
3. *When will the dataset be distributed?*
  - The datasets used in this paper is distributed in 2022.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset is distributed under a MIT license.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No restrictions are placed on the dataset.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- None.
7. *Any other comments?*
	- None.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Tian Yi Zhang is hosting the dataset on the github link at https://github.com/zhan7818/bdo_monetization.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The creator of the datasets, Tian Yi Zhang, can be contacted at tianyi.zhang6546@gmail.com.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- As of writing this datasheet, no explicit erratum have been spotted.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Any updates will be posted on the github page used to host this paper which include the datasets.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the datasets (if there will be any) will be kept as a record on github.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- One should contact Tian Yi Zhang, the author of the dataset.
8. *Any other comments?*
	- None.

>>>>

---
title: The nature that determine an anime show's popularity involves the source material of the adaptation and the years it was released.
author: 
  - Justin Abando
thanks: "Code and data are available at: https://github.com/justabando/malanalysis."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "There are online lists and forums where users can vote on what they believe to be the most popular anime such as MyAnimeList (MAL). However, there are no metrics that can determine why specific anime stand out, and so data was retrieved to determine what factors could be responsible for a show's popularity. It was found that the source material and year of the anime's release were significant in determining how many users of MAL watched the anime. The findings of this paper suggests reasons why a particular anime becomes popular, which can be relevant to those that are new to watching anime or those that want something new to watch as they would gravitate to shows that receive traction by a broader demographic."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(dplyr)
library(broom)
library(ggplot2)
library(knitr)
library(kableExtra)

@@

  This presents two ways for newcomers to judge a show before watching. They can be inclined to start a show that is subjectively rated as one of the best as ranked by the MAL community, or choose one that has gained the most traction despite any apparent flaws or drawbacks that may deter a positive watching experience. As such, it should be noted that popularity is not a metric that is inherently positive, but can also imply the notorious status of a show, especially if it is ranked low in terms of rating but manages to be much more popular than its rating score suggests. This creates an interesting method to identify shows that have managed to be popular despite its poor ranking performance. It could be that the show has notoriously bad traits that often gets shared to others to ridicule or prank unsuspecting friends to watch and experience a show that can be "so bad that its good". The anime may have been able to maintain a good quality throughout its run time, but eventually hit a point in the plot that polarizes the show's watchers. Regardless, there are many ways to interpret the collective opinion of a show on MAL with the presence of ranking both its ratings and popularity. While the rating of a show is indicative of how well-received the show is strictly by the subject and content of the show itself, the popularity of a show can be shrouded in mystery and depend on many logistical factors the put an anime in the limelight.

@@

  It was found that the source material of the anime that it was adapted into had a significant impact on MAL viewership of anime, as shown with a linear regression model found in @sec-model. Additionally, ___________.

  The findings of this paper suggest that the popularity of a show is influenced by a variety of factors that may not be obvious by just watching the show itself. These findings can help someone who is new to watching anime, or those that want something new to watch to find something that gained traction within the community. Popularity can be a factor that is more important than the ranking of the show's quality in many cases, and this is due to the context that the show presents. An anime may be very well-received, but it may be less known within the broader community. With less overall viewership of an anime, the show may still be ranked relatively high in terms of rating due to its niche community that watches the show, which can inflate its overall ranking in its ratings. This is why ratings are not necessarily the best metric to depend on for newcomers to find a show to watch, as a niche show may not be widely accessible to a broad audience. However, popularity ranking can be much more indicative of a potential show someone can watch due to its exposure that is not dependent on the taste or bias of the viewer.

@@

Regardless, data from MAL was imported and analyzed in R [@r2023]. To aid in this analysis, the `dplyr` [@wickham2023] and `ggplot2` [@wickham2016] packages from the `tidyverse` package [@wickham2019] were used to clean the data set and generate graphs to visualize it respectively. The `knitr` [@xie2021] and `kableExtra` [@zhu2021] packages were used to create the tables used within this analysis. The table used to generate the summary of the regression analysis was tidied using the `broom` package [@robinson2023].

@@

* `title`: the title of the anime.
* `type`: the medium of how the anime is delivered (e.g. tv show, movie, etc.).
* `score`: aggregated score of the anime out of 10, contributed by users of MAL that both have the anime in their list as well as rated it numerically out of 10.
* `scored_by`: the number of MAL users that have the anime in their list and rated the anime out of 10.
* `members`: the number of MAL users that have the anime in their list.
* `episodes`: the number of episodes that a given anime has.
* `source`: the type of source material that the anime was adapted from (e.g. manga, light novel, anime original, etc.).
* `start_year`: the year in which the anime first started to broadcast.

The important variable of note to consider from this list is `members`. This is a quantitative variable that popularity ranking on MAL is completely dependent on. The popularity ranking of an anime is directly affected by how many members an anime has, and so an anime that has the most members would have the #1 popularity ranking. Other than `title`, the rest of the variables will be tested to see if they have any kind of influence on the amount of users that have specific shows on their lists.

@@

animeinformationsummary |>
  kable(
    caption = "Sample from the top rated anime of MAL, which includes the information of each anime itself.",
    col.names = c("Rank",
                  "Title",
                  "Show Type",
                  "Episode Count",
                  "Source Material",
                  "Start Year"),
    booktabs = TRUE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(font_size = 10) |>
  column_spec(2, width = "5cm") |>
  column_spec(3, width = "1cm") |>
  column_spec(4, width = "2cm") |>
  column_spec(5, width = "2.5cm") |>
  column_spec(6, width = "1cm")

@@

The main variables of interest as mentioned previously are medium of the show, episode count, source material, initial release year, and studio. These are all important and can possibly influence the popularity of an anime without giving any actual information of what the anime is about.

A linear regression model can be used to predict how each of the qualitative independent factors can affect how many users of MAL watch a given anime. One particular variable of note to be examined is the source material of the show, as there is the consideration of fans of the source work of the anime adaptation. Those that follow the source material would naturally have some level of interest in an anime adaptation, and so this model accounts for how significant the source material is in influencing MAL viewership of a show.

The following linear regression model was created below to illustrate this:

$$
\text{MAL Viewership} = \beta_0 + \beta_1 \cdot \text{Source Material} + \epsilon
$$
With this model uses the following components:

* $\beta_0$: The intercept of the regression line.

* $\beta_1$: The coefficient representing the relationship between source material and members of an anime.

* $\epsilon$: The residual or error term.

Table 3 illustrates the results of the linear regression modelling, where it is seen that several popular source material formats had a significantly low p-value, suggesting there is a correlation between the type of source material the anime is adapted from and MAL viewership. Prominent source material formats such as manga, light novels, and original anime all have p-values less than 0.05, suggesting there is a correlation between the two variables.

#|label: tbl-regressionmodel
#|message: false
#|warning: false

anime_model <- lm(members ~ source, data = cleanedanime2)

tidy_anime_model <-
  anime_model |>
  summary() |>
  tidy()

tidy_anime_model |>
  kable(
    digits=4, 
    align = "c", 
    caption = "Linear regression model summary statistics of the impact of source material on MAL user viewership",
    col.names = c("Source Type",
                  "Estimate",
                  "Std. Error",
                  "Test Statistic",
                  "P-value"),    
    booktabs = TRUE,
    linesep = "", 
  )

## Show Type

To visualize how the medium of the anime affects MAL viewership, @fig-membertype demonstrates the influence of format. The most common format is TV anime, followed closely by movie anime. When looking at the MAL members that have watched it, it is observed that the majority of users watch shows within those formats.

```{r}
#| label: fig-membertype
#| fig-cap: Visualization of how many MAL users viewed an anime based on the medium that it was presented in. The most popular mediums to produce anime in are movies and in TV shows, which is reflected with how many MAL users viewed anime in those specific categories. For reference, music anime refers to music videos presented in an anime artstyle, ONA is an original anime special included in DVD or Blu-Ray releases of an anime, OVA is an original video anime released exclusively online, and special anime are extra episodes attached to an already established series.
#| echo: false
#| message: false
#| warning: false

ggplot(
  cleanedanime2, aes(
    x=type,
    y=members
    )
  ) + geom_point(
    aes(colour = type), #Adding colour to differentiate each show type
    alpha = 0.50 
  ) + 
  labs(
    x = "Show Type",
    y = "Members"
  )

## Episode Count

Episode count is also a factor that may affect how many MAL users would view a specific show. This is visualized in @fig-memberepisode, where the length of a series impacts MAL viewership. It is seen that many shows with episodes around 1, 12-13 and 24-26 have the most MAL viewership by users.

```{r}
#| label: fig-memberepisode
#| fig-cap: Visualization of how the episode count of an anime can influence MAL user viewership. There are areas with many specific peaks in viewership, most notably at the 1 episode, 12-13 episode, and 24-26 episode mark, which likely would pertain to movies and seasonal anime. 
#| echo: false
#| message: false
#| warning: false

ggplot(
  cleanedanime2, aes(
    x=episodes,
    y=members
    )
  ) + geom_point(
    alpha = 0.50) + 
  xlim(0, 100) +
  labs(
    x = "Episodes",
    y = "Members"
  )

## Source Material

The importance of the source material of an anime as explained in @sec-model is visualized in @fig-membersource. Many types of source material adaptations are present, with the most important ones to note being manga, light novels, and originals, which have the most MAL user viewership than any other source material disregarding outliers.

```{r}
#| label: fig-membersource
#| fig-cap: The influence of source material in MAL user viewership. Manga has the most pronounced and highest viewership of any other source material, followed closely by light novels and original anime.
#| echo: false
#| message: false
#| warning: false

ggplot(
  cleanedanime2, aes(
    x=source,
    y=members
    )
  ) + geom_point(
    aes(colour = source), #Adding colour to differentiate each show type
    alpha = 0.50 
  ) + labs(
    x = "Source Material",
    y = "Members"
  ) + theme(axis.text.x = element_text(angle = 90))

## Year of Release

A visualization of how viewership is impacted depending on how old an anime is can be seen in @fig-memberyear. It can be seen that there are considerable more entries of anime in general, as more shows were produced in the 1970s. However, there does seem to be more MAL users that watch shows around past the year 2000 mark. Meanwhile, MAL viewership for anime produced before 1975 are rarely seen in comparison.

@@

@@

## Show Type

##

@@

There are many limitations that are present in this statistical analysis. First, the depth of information is vast as there are many other variables that can be considered when determining the popularity of an anime. Factors from the production side such as the studios that produced the anime, to licensors that release the show on platforms to be watched on are also important for gathering attention to shows. In addition, factors that may give more information about what the show might be about such as the genres and themes may also play an important role as personal appeaal to specific genres may help gravitate MAL users to watch particular shows.

Another consideration that has to be made is in regards to

@@

	- Each instance in the dataset represent an anime entry within the MAL database since July 2022. 

@@

	- There are a total of 11,890 observations, each representing a different show.

@@

	- The dataset contains a sample of instances from the total shows available on the MAL database which can be accessed from the official MAL API. The last update to this dataset that was obtained was on July 2022, and is not indicative of all of the instances that may have been added between then and the time of this paper being published. Additionally, the dataset was cleaned to include instances that had all of the necessary variables to conduct statistical analysis on in this project. 

@@

	-  Each instance of data consists of the title of the show, score of the show, how many MAL users added it to their list, how many MAL users rated it, medium of the show, episode count, source material, start year, and studio that produced the show.

@@

	- The label of each instance is an anime.

@@

	- N/A

@@

	- Some relationships between individual instances are made explicit, for example when a show has a movie with the prefix of the movie title being the show's name. It is also made explicit for sequels of anime or spin-offs that include the main title of the original showl.

@@

	- N/A

@@

	- Some instances of the dataset do not contain any information, which affect how many shows could be analyzed in this report.

@@

	- All of the data within the dataset is publicly available information on the MAL website.

@@

	- The dataset does contain keywords that may be offensive or insulting depending on the titles, themes, and descriptions of the instances.

@@

	- N/A

@@

	- N/A

@@

	- The dataset does not contain data that could be considered sensitive.

@@

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was collected via Kaggle and was directly observable, with variables and values explicitly visible.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data was manually curated by combining two APIs, MAL and Jikan to obtian all of the relevant information within the dataset.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- N/A
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Only the original author, Andreu Vall Hernandez, was involved in the data collection process.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data was last collected on July 25th, 2022, with older versions extending as far back as June 21st, 2022.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No ethical review processes were conducted.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected from a third-party source, Kaggle.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- The individual who created the dataset was not notified about the data collection.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- The individual who created the dataset did not give any consent to the collection of the data that was gathered, however it was made available on Kaggle for use by the public, and included their GitHub repo to demonstrate how they collected the data for reproducibility.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- N/A
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- N/A.
12. *Any other comments?*
	- None.

@@

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Variable names were renamed to be more clear, and the dataset was trimmed down to only include pertinent variables required for the analysis.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- The raw data is accessible via the GitHub repo on the first page of the report.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- Statistical programming language R [@r2023] was used to preprocess, clean, and label the data.
4. *Any other comments?*
	- None.

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- It is unknown if the dataset has been used by others as the dataset was made publicly available for anyone to use.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The repository for how the dataset was created are available at https://github.com/andreu-vall/myanimelist-api-scraping
3. *What (other) tasks could the dataset be used for?*
	- The dataset can be used for analysis of different factors, or for different analytic reasons than the one described in this report. Much of the data pertains to information only present on MAL, so any kind of analysis on MAL could be done with this dataset.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- None.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- None, all of the data present within the dataset is publicly available information on the MAL webite, the dataset simply aggregates all of that information into one file.
6. *Any other comments?*
	- None.

@@

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Yes, as the GitHub repo will be made public.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The dataset is distributed on the GitHub repo: https://github.com/justabando/malanalysis. There is no DOI.
3. *When will the dataset be distributed?*
  - The datasets used in this paper will be distributed in April 2023.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- The dataset that was created for this paper is distributed under a MIT license. The original dataset is licensed under CC 1.0 Universal Public Domain Dedication.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No restrictions are placed on any of the datasets used or created for this report.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- None.
7. *Any other comments?*
	- None.

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Justin Abando will host, maintain, and support the dataset at https://github.com/justabando/malanalysis.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- The original creator of the dataset, Andreu Vall Hernandez, can be contacted at andreu.vallhernandez@gmail.com. The author of this paper, Justin Abando, can be contacted at justin.abando2@gmail.com.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- N/A
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Any updates will be posted on the GitHub repo used to host this paper which include the datasets.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions of the datasets will be available on the GitHub repo.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Anyone that wants to contribute to the original dataset should contact Andreu Vall Hernandez at andreu.vallhernandez@gmail.com.
8. *Any other comments?*
	- None.
